---
title: "Global Rc"
output: html_notebook
---

# Introduction

This checks the pixel_work function visually.

## Goals

```{r load_libraries}
library(dplyr)
library(futile.logger)
library(plotrix)
library(pracma)  # "practical math" alternative interpolation.
library(rprojroot)
library(viridis)
library(globalrc)
library(rampdata)
invisible(flog.threshold(INFO))  # Set to DEBUG if you want to see messages.
proj_root <- rprojroot::find_root(rprojroot::is_git_root)
config <- file.path(proj_root, "scripts", "rc_kappa.toml")
rampdata::initialize_workflow(config)
```

```{r plot_set_up}
make_colors <- function() {
  col <- viridis::plasma(7, alpha = 1, begin = 0, end = 1)
  c(pfpr = col[1], am = col[2], alpha = col[3], kappa = col[4], aeir = col[5],
       vc = col[6], rc = col[7])
}
mcol <- make_colors()
var_names <- c("alpha", "kappa", "aeir", "vc", "rc")
var_colors <- mcol[var_names]
```

## Initialization

Austin made a map from PR and rho to AR. We will use that function,
so load the data he calculated, and create an interpolation function.
```{r read_script}

# Load the data that Austin made, turning it into a function.
local_pr2ar <- as.path(workflow_path("pr2ar"))
if (!file.exists(local_pr2ar)) {
  local_pr2ar <- file.path("..", local_pr2ar)
  flog.debug("looking for pr2ar up a directory", local_pr2ar)
}
pr_to_ar_dt <- data.table::fread(local_pr2ar)
params <- configr::read.config(config)$parameters
show_df <- data.frame(params)
strategies <- list(
  pr_to_ar = ar_of_pr_rho(pr_to_ar_dt),
  ar2pr = globalrc::build_ar2pr(pr_to_ar_dt)
)
show_df
```

## The main function

```{r}
# Lets me make a copy of parameters with some changes.
set_params <- function(p, ...) {
  ll <- list(...)
  p[names(ll)] <- ll
  p
}
params2 <- set_params(params, kam = 0.6)
data.frame(params2[vapply(params2, is.numeric, logical(1))])
```

Make a table of values with the draws. That means we set the two inputs,
pfpr and rho. Then we generate draws of parameter values, run the function
against the inputs and parameter values, and summarize the results with
mean and quantiles.
```{r table_with_draws}
pfpr <- seq(0.02, 0.98, 0.02)
rho <- seq(0, 0.5, 0.1)
df <- data.frame(list(pfpr = rep(pfpr, length(rho)), rho = rep(rho, each = length(pfpr))))
df$am <- df$rho / params$kam
sample_cnt <- nrow(df)
draw_cnt <- 100000
draw_params <- draw_parameters(params2, draw_cnt)

over_draws <- lapply(1:draw_cnt, function(draw_idx) {
  pixel_four(df$pfpr, df$am, draw_params[draw_idx, ], strategies)
})
var_names <- names(over_draws[[1]])
for (single_var in var_names) {
  single_arr <- vapply(over_draws, function(one_draw) {
    one_draw[[single_var]]
  }, FUN.VALUE = numeric(sample_cnt))
  dim(single_arr)
  single_summary <- list(
    mean = apply(single_arr, c(1), mean),
    median = apply(single_arr, c(1), function(x) quantile(x, 0.5)),
    lower = apply(single_arr, c(1), function(x) quantile(x, 0.025)),
    upper = apply(single_arr, c(1), function(x) quantile(x, 0.975)),
    max = apply(single_arr, c(1), max),
    min = apply(single_arr, c(1), min)
  )
  names(single_summary) <- sprintf("%s_%s", single_var, names(single_summary))
  df <- cbind(df, single_summary)
}
rc_only <- df[, startsWith(names(df), "vc_")]
data.table::fwrite(df, file = file.path(proj_root, "notebooks", "pixel_four.csv"))
df
```

```{r load_once}
original <- load_pixel_script(file.path(proj_root, "R", "estimate_rc_script.R"))

```

```{r for_comparison}
# draw_cnt <- 1000 # from above
vals <- vapply(seq(0.02, 0.98, 0.02), function(pfpr) {
  all_out <- original$pr2rcS(rep(pfpr, draw_cnt), Short = FALSE)
  keep <- cbind(pfpr = pfpr, kappa = all_out$kappa, rc = all_out$Rc, aeir = all_out$aeir)
  apply(keep, 2, median)
}, FUN.VALUE = numeric(4))
original_df <- data.frame(t(vals))
```

```{r compare_original}
df2 <- df[df$rho == 0.0, c("kappa_median", "rc_median", "aeir_median")]
names(df2)[names(df2) %in% c("kappa_median", "rc_median", "aeir_median")] <- c(
  "kappa", "rc", "aeir"
)
relerr <- function(a, b) { (a - b) / b }
list(
rc = max(relerr(df2$rc, original_df$rc)),
aeir = max(relerr(df2$aeir, original_df$aeir)),
kappa = max(relerr(df2$kappa, original_df$kappa))
)
```


```{r}
rho0 <- 0.5
nearly <- function(a, b) { abs(a-b) < 1e-7 }
pfpr_one_rho <- df[nearly(df$rh,rho0), ]
with(pfpr_one_rho, {
  plot(pfpr, arnotreat_median, main = sprintf("rho=%3.2f", rho0))
})
```

