---
title: "Global Rc"
output: html_notebook
---

# Introduction

We need to work with the function that derives an R_c from PfPR and
treatment. The function that does the core of the calculation is
in the `rc_kappa.R` file, so we will source that file and work with
the function on test data.

## Goals

1. Deliver $R_c$ for multiple draws of parameters (specifically, $k$ in the EIR),
   as a median surface, with C.I. bounds, so three surfaces.
  
## Steps

1. Calculate EIR directly from PfPR using a fit. It's a parametrized log-linear
   fit, so this means making a csv with the numbers and uncertainty.
   
2. Calculate effect of case management by computing a shift.
   
   1. The shift is, shift(pr, rho) = pr2ar(pr, 0) - pr2ar(pr, rho).
   2. Apply that shift to alpha, as back-calculated from EIR, to FOI, to alpha. Then forward-calculate
      to get a new EIR.

3. More steps to tune equations. For instance, what's the constant
   for rho = k_am * am?

4. Modify $r$ in $D=c/r$ by the AM.

5. Use a cutoff (PR<0.10, EIR<0.5) to choose when to switch to a low-intensity set
   of equations. Write down those equations.
   
6. Change the `rc_kappa.R` code to work over draws of parameters and save
   median and C.I. surfaces.

7. Run with draws. Do a test patch to gauge speed, then run.

```{r load_libraries}
library(akima)
library(dplyr)
library(futile.logger)
library(plotrix)
library(pracma)  # "practical math" alternative interpolation.
library(rprojroot)
library(viridis)
invisible(flog.threshold(INFO))  # Set to DEBUG if you want to see messages.
```

```{r plot_set_up}
make_colors <- function() {
  col <- viridis::plasma(7, alpha = 1, begin = 0, end = 1)
  c(pfpr = col[1], am = col[2], alpha = col[3], kappa = col[4], aeir = col[5],
       vc = col[6], rc = col[7])
}
mcol <- make_colors()
var_names <- c("alpha", "kappa", "aeir", "vc", "rc")
var_colors <- mcol[var_names]
```

## Initialization

Austin made a map from PR and rho to AR. We will use that function,
so load the data he calculated, and create an interpolation function.
```{r read_script}
# The Akima interpolation is meant to interpolate from one grid to another.
# Our destination points aren't a grid, so it's the wrong one to use.
# It's OK for a single point, though, so can use it for checking the other one.
ar_of_pr_rho2 <- function(pr_to_ar_dt) {
    dt <- pr_to_ar_dt
    function(pr, rho) {
        akima::interp(x = dt$rho, y = dt$PR, z = dt$AR, xo = rho, yo = pr,
        extrap = TRUE)[[3]]
    }
}
ar_of_pr_rho <- function(pr_to_ar_dt) {
  if (length(unique(pr_to_ar_dt$rho[1:5])) < 5) {
    flog.debug("PR moves faster in pr_to_ar mesh file.")
    dtrow <- sort(unique(pr_to_ar_dt$PR))
    dtcol <- sort(unique(pr_to_ar_dt$rho))
    dtz <- array(pr_to_ar_dt$AR, dim = c(length(dtrow), length(dtcol)))
    function(pr, rho) {
      # This call looks like x and y are mixed up, but check the tests below.
      pracma::interp2(dtcol, dtrow, dtz, xp = rho, yp = pr, method = "linear")
    }
  } else {
    flog.debug("rho moves faster in pr_to_ar mesh file.")
    dtrow <- sort(unique(pr_to_ar_dt$rho))
    dtcol <- sort(unique(pr_to_ar_dt$PR))
    dtz <- array(pr_to_ar_dt$AR, dim = c(length(dtrow), length(dtcol)))
    function(pr, rho) {
      pracma::interp2(dtcol, dtrow, dtz, xp = pr, yp = rho, method = "linear")
    }
  }
}
# Load the data that Austin made, turning it into a function.
local_pr2ar <- "pr2ar_mesh.csv"
local_pr2ar <- "~/data/projects/globalrc/outputs/pr2ar_mesh/201105/pr2ar_mesh.csv"
if (!file.exists(local_pr2ar)) {
  local_pr2ar <- file.path("..", local_pr2ar)
  flog.debug("looking for pr2ar up a directory", local_pr2ar)
}
pr_to_ar_dt <- data.table::fread(local_pr2ar)
pr_to_ar <- ar_of_pr_rho(pr_to_ar_dt)
for (test_line in c(5, 20, 42)) {
  egval <- pr_to_ar_dt[5]
  relerr <- (pr_to_ar(egval$PR, egval$rho) - egval$AR) / egval$AR
  stopifnot(relerr < 0.01)
}
params <- list(
  kam = 0.6,  # multiplier by am to get rho
  b = 0.55,
  b_shape1 = 55,
  b_shape2 = 45,
  c = 0.17,
  k = 4.2,
  ku = 0.5, # quantile of draw
  r = 0.005,  # recovery without treatment
  r_sd = 0.0003333333,  # 1/3000
  tau = 10,  # time step days for FOI
  D_low = 5,  # days with treatment
  D_high = 40,  # days without treatment
  random_seed = 24243299,
  confidence_percent = 95
  )
show_df <- data.frame(params)
params$pr_to_ar <- pr_to_ar
show_df
```

Will the pr2ar data work for getting pr from ar from rho=0?
```{r ar2pr_same_data}
zero_row <- pr_to_ar_dt[rho < 1e-6,c("PR", "AR")]
plot(zero_row$AR, zero_row$PR)
```
```{r interp_zero_row}
attack_rates <- c(0, 1e-4, 0.015, 0.3, 0.5, 0.4, 0.937,max(zero_row$AR)+1e-4, 0.99)
make_ar2pr <- function(pr_ar_data) {
  no_treatment <- pr_ar_data[rho < 1e-6, c("PR", "AR")]
  # The sample data doesn't go all the way to 0 and 1, but that's the asymptotic value.
  AR_sample <- c(0, no_treatment$AR, 1)
  PR_sample <- c(0, no_treatment$PR, 1)
  function(attack_rates) {
    pracma::interp1(AR_sample, PR_sample, attack_rates, method = "linear")
  }
}
params$ar2pr <- make_ar2pr(pr_to_ar_dt)
xar <- seq(0.01, 0.99, 0.01)
plot(xar, params$ar2pr(xar), log = "x")
```

If we use Cronus to ask what PfPR would be without treatment, what does
it say for different levels of treatment?
```{r adjusted_pr}
untreat_pfpr <- function(pfpr, rho) {
    alpha_cronus <- pr_to_ar(pfpr, rho)
    params$ar2pr(alpha_cronus)
}
plot(
  numeric(0), numeric(0), xlim = c(0, 1), ylim = c(0, 1),
  xlab = "PfPR", ylab = "Putative Untreated PfPR",
  main = "Putative Untreated PfPR to PfPR"
  )
pfpr <- seq(0.01, 0.99, 0.01)
am_vals <- c(0, 0.02, 0.1, 0.3, 0.6) / params$kam
amcol <-   col <- viridis::plasma(length(am_vals), alpha = 1, begin = 0, end = 1)
for (am_idx in seq_along(am_vals)) {
  am0 <- am_vals[am_idx]

  am <- rep(am0, length(pfpr))
  lines(pfpr, untreat_pfpr(pfpr, am), col = amcol[am_idx])
}
legend("bottomright", legend = as.character(am_vals),
       col = amcol[1:length(am_vals)], lty = 1, lwd = 2, cex = 1,
       title = "Rho Values")
```
```{r difference_in_treated_untreated}
plot(
  numeric(0), numeric(0), xlim = c(0, 1), ylim = c(0, 0.3),
  xlab = "PfPR", ylab = "Addition to PfPR",
  main = "Difference in Treated and Untreated PfPR"
  )
pfpr <- seq(0.01, 0.99, 0.01)
rho_vals <- seq(0, 0.8, 0.2)
rhocol <-   col <- viridis::plasma(length(rho_vals), alpha = 1, begin = 0, end = 1)
for (rho_idx in seq_along(rho_vals)) {
  rho0 <- rho_vals[rho_idx]

  rho <- rep(rho0, length(pfpr))
  diff <- untreat_pfpr(pfpr, rho) - pfpr
  lines(pfpr, diff, col = rhocol[rho_idx])
}
legend("topright", legend = sprintf("%3.2f", rho_vals),
       col = rhocol[1:length(rho_vals)], lty = 1, lwd = 2, cex = 1,
       title = "Rho Values")
```


## The main function

```{r pr2eir_fit}
# Functional form. This could be EIR around home, "local EIR".
# Returns daily EIR. Multiply by 365 for annual.
pr2eir=function(x, b=0.55, r=1/200, k=4.2){
  ((1-x)^-k-1)*(r/k/b)
}
# Same, but with random parameters.
# deir = daily EIR. aeir = annual. leir = log(annual EIR).
pr2eirS = function(x, n=1){
  pr = rep(x, each=n)
  r = rnorm(length(pr), 1/200, 1/3000)
  k = rgamma(length(pr), 4.2*(1-pr)^.6*5, 5*(1-pr)^.6)
  b = rbeta(length(pr), .55*100, .45*100)
  eir = pmin(((1-pr)^-k-1)*(r/k/b), 1500/365)
  cbind(pr=pr, deir=eir, aeir=eir*365, leir = log10(eir*365))
}
# log-linear. This is "total EIR."
# Annual EIR.
pr2eir.llin = function(x){
  leir = -0.262776 + 3.213*x
  eir = 10^leir
  cbind(pr=x, logeir = leir, eir=eir)
}
pr2eir.llinS = function(x, n=1){
  pr = rep(x, each=n)
  leir = -0.262776 + 3.213*pr + rnorm(length(pr),0,.53)
  eir = 10^leir
  cbind(pr=pr, logeir = leir, eir=eir)
}
show_pr2eir <- function() {
  x <- seq(0.01, 0.99, 0.01)
  plot(
    x, pr2eir(x),
    xlim = c(0, 0.98), log = "y", ylab = "PfEIR", xlab = "PfPR",
    main = "pr2eir function"
    )
}
show_pr2eir()
```
```{r from_pr_to_eir}
pfpr <- seq(0.01, 0.99, 0.01)
eir <- with(params, pmin(365*pr2eir(pfpr, b, r, k), rep(1500, length(pfpr))))
plot(pfpr, eir, main = "Yearly PfEIR with a Cutoff at Max Ever Seen",
     type = "l", log = "y", yaxt = "n")
order_labels <- c("0.1", "1.0", "10", "100", "1000")
axis(2, at = as.numeric(order_labels), labels = order_labels)
```
Check that our equations from eir to alpha and back to eir are correct.
```{r the_way_from_eir_to_alpha_and_back}
eir_nt <- 10
eir <- with(params, {
#alpha_nt <- 1 - exp(-log(1 + eir_nt * k * tau) / k)
h_tau <- log(eir_nt *  (b * k * tau) + 1) / k
alpha_nt <- 1 - exp(-h_tau)
alpha_nt <- 1 - (eir_nt * b * k * tau + 1)^(-1/k)
h <- -log(1 - alpha_nt) / tau
# h <- log(eir_nt * b * k * tau + 1) / (k * tau)
(exp(h * k * tau) - 1) / (b * k * tau)
})
c(eir_nt, eir)
```


I'll copy the main function here so we can work with it.
```{r pixel_work_copy}
kappa_rm <- function(pfpr, c) { c * pfpr }
alpha_cronus <- function(pfpr, k, rho, tau) pr_to_ar(pfpr, rho)
alpha_from_eir <- function(pfpr, k, rho, tau) {
  eir <- pr2eir(pfpr, b, r, k)
  alpha <- 1 - (eir_nt * b * k * tau + 1)^(-1/k)
  alpha + pr_to_ar(pfpr, rho) - pr_to_ar(pfpr, 0)
}
rc_basic <- function(b, c, r, V, am) { b * V * c / r }
strategies <- list(
  alphaf = alpha_from_eir, kappaf = kappa_rm, rcf = rc_basic, ar2pr = make_ar2pr(pr_to_ar_dt),
  pr_to_ar = pr_to_ar
  )

pixel_try <- function(pfpr, am, params, strategies) {
  # PfPR and AM come in with the same set of NA patterns, where there is no land.
  with(c(params, strategies), {
    alpha <- alphaf(pfpr, k, kam * am, tau)
    kappa <- kappaf(pfpr, c)
    h <- -log(1 - alpha) / tau
    eir <- (exp(h * k * tau) - 1) / (b * k * tau)
    V <- eir / kappa
    R <- rcf(b, c, r, V, am)
    list(
      alpha = alpha,
      kappa = kappa,
      deir = eir,
      vc = V,
      rc = R
    )
  })
}
# Here, we don't worry about the strategies. Write everything out where
# we can see it.
pixel_two <- function(pfpr, am, params, strategies) {
  # PfPR and AM come in with the same set of NA patterns, where there is no land.
  with(c(params, strategies), {
    rho <- kam * am
    kd <- qgamma(params$ku, k * (1 - pfpr)^.6 * 5, 5 * (1 - pfpr)^.6)
    # We aren't using the mechanistic model to get an absolute value of alpha
    # because that alpha isn't close enough. We are using that model to
    # estimate how much treatment would shift PfPR, given an alpha.
    alpha_cronus <- pr_to_ar(pfpr, rho)
    # nt = no_treatment
    pfpr_nt <- ar2pr(alpha_cronus)
    # This EIR estimate is from a fit to data.
    max_deir <- 1500 / 365
    eir_nt <- pmin(
      pr2eir(pfpr_nt, b, r, kd),
      rep(Inf, length(pfpr_nt))
      )
    alpha_nt <- 1 - (eir_nt * b * kd * tau + 1)^(-1/kd)
    # Then go back and estimate how much treatment would mean alpha was higher.
    lower_ar <- pr_to_ar(pfpr, numeric(length(pfpr)))
    upper_ar <- pr_to_ar(pfpr, rho)
    # Move it the same relative distance to the upper bound.
    alpha <- 1 - (1 - alpha_nt) * (1 - upper_ar) / (1 - lower_ar)

    kappa <- c * pfpr_nt
    h <- -log(1 - alpha) / tau
    # alpha can be 1 after the shift, so cap FOI.
    # These will be infinite, and that's OK. We don't
    # get rid of NAN. Those are failures.
    max_finite <- 1e10
    h[h > max_finite] <- max_finite
    eir <- (exp(h * kd * tau) - 1) / (b * kd * tau)
    eir[eir > max_finite] <- max_finite
    V <- ifelse(
        kappa > 0,
        eir / kappa,
        0
    )
    V[V > max_finite] <- max_finite
    R <- b * V * ((1 - rho) * D_high + rho * D_low)
    R[R > max_finite] <- max_finite
    list(
      alpha = alpha,
      kappa = kappa,
      foi = h,
      # deir = daily eir, aeir = annual eir = 365 * deir.
      aeir = eir * 365,
      vc = V,
      rc = R
    )
  })
}
```

The parameters should be drawn from a distribution. So you take params,
as defined above, and put them into here to get the draws.
```{r parameters_as_draws}
#' Takes a parameter that is an expression (of drawing a distribution) and calls it.
draw_parameters <- function(parameters, N) {
    if (N > 1) {
        draw_params <- with(parameters, {
            data.frame(
                kam = rep(kam, N),
                r = rnorm(N, r, r_sd),
                k = k,
                ku = runif(N),  # Use as quantile within calculation.
                b = rbeta(N, b, b_shape1, b_shape2),
                c = rep(c, N),
                tau = rep(tau, N),
                D_low = rep(D_low, N),
                D_high = rep(D_high, N)
            )
        })
    } else {
        draw_params <- data.frame(
            kam = kam,
            r = r,
            k = k,  # mean for k calculation.
            ku = 0.5,  # Use as quantile within calculation.
            b = b,
            c = c,
            tau = tau,
            D_low = D_low,
            D_high = D_high
        )
    }
    # If any parameters are less than zero, we should redraw.
    # It's a rejection method to get truncated distributions.
    stopifnot(all(as.matrix(draw_params) > 0))
    draw_params
}
```

```{r}
set_params <- function(p, ...) {
  ll <- list(...)
  p[names(ll)] <- ll
  p
}
params2 <- set_params(params, kam = 0.6)
data.frame(params2[vapply(params2, is.numeric, logical(1))])
```

Make a table of values with the draws. That means we set the two inputs,
pfpr and rho. Then we generate draws of parameter values, run the function
against the inputs and parameter values, and summarize the results with
mean and quantiles.
```{r table_with_draws}
pfpr <- c(0.05, seq(0.1, 0.5, 0.1))
rho <- seq(0, 0.5, 0.1)
df <- data.frame(list(pfpr = rep(pfpr, length(rho)), rho = rep(rho, each = length(pfpr))))
df$am <- df$rho / params$kam
sample_cnt <- nrow(df)
draw_cnt <- 10000
draw_params <- draw_parameters(params2, draw_cnt)

over_draws <- lapply(1:draw_cnt, function(draw_idx) {
  pixel_two(df$pfpr, df$am, draw_params[draw_idx, ], strategies)
})
var_names <- names(over_draws[[1]])
for (single_var in "rc") {
  single_arr <- vapply(over_draws, function(one_draw) {
    one_draw[[single_var]]
  }, FUN.VALUE = numeric(sample_cnt))
  dim(single_arr)
  single_summary <- list(
    trimmed = apply(single_arr, c(1), function(x) mean(x, trim = 0.2)),
    mean = apply(single_arr, c(1), mean),
    median = apply(single_arr, c(1), function(x) quantile(x, 0.5)),
    lower = apply(single_arr, c(1), function(x) quantile(x, 0.025)),
    upper = apply(single_arr, c(1), function(x) quantile(x, 0.975))
  )
  names(single_summary) <- sprintf("%s_%s", single_var, names(single_summary))
  df <- cbind(df, single_summary)
}
data.table::fwrite(df, file = "summary_median_rc.csv")
df
```



How about making a table of values.
```{r create_table_of_values}
pfpr <- c(0.01, 0.1, 0.2, 0.3, 0.4, 0.8)
am <- c(0.00, 0.02, 0.3, 0.6)
df <- data.frame(list(pfpr = rep(pfpr, length(am)), am = rep(am, each = length(pfpr))))
res <- vapply(
  1:nrow(df),
  function(row) {
    ll <- pixel_two(df$pfpr[row], df$am[row], params, strategies)
    setNames(as.numeric(ll), names(ll))
    },
  FUN.VALUE = numeric(8)
  )
cbind(df, t(res))
```


```{r inset_rc, eval = FALSE}
inset_rc <- function(pfpr, rc) {
  u <- par("usr")
  v <- c(
    grconvertX(u[1:2], "user", "ndc"),
    grconvertY(u[3:4], "user", "ndc")
  )
  v <- c( (v[1]+v[2])/2, v[2], (v[3]+v[4])/2, v[4] )
  par( fig=v, new=TRUE, mar=c(0,0,0,0) )
  plot(pfpr, rc, axes=TRUE, xlab="", ylab="")
  box()
}
```

Plot annual EIR (i.e. multiply daily EIR by 365) vs PR, and plot on a log10 scale.
```{r annual_eir, fig.height = 5, fig.width = 10}
pfpr <- seq(0.01, 0.99, 0.01)
par(mfrow = c(2, 2))
for (am0 in c(0.0, 0.01, 0.1, 0.3)) {
am <- rep(am0, length(pfpr))
k_is_one <- function(p) {
  p$kam <- 1.0
  p
  }
vars <- pixel_two(pfpr, am, k_is_one(params), strategies)
plot(
  vars$aeir, pfpr,
  main = sprintf("rho = %3.2f", am0), xlab = "EIR [annual log10]", ylab = "PfPR",
  log = "x", type = "l", col = var_colors["aeir"]
)
}
```

```{r annual_eir_shift, fig.height = 5, fig.width = 7}
pfpr <- seq(0.01, 0.99, 0.01)
k_is_one <- function(p) {
  p$kam <- 1.0
  p
  }
#par(mfrow = c(1, 2))
amcol <- viridis::plasma(7, alpha = 1, begin = 0, end = 1)
am0 <- 0.0
am <- rep(am0, length(pfpr))
plot(
  numeric(0), numeric(0),
  xlim = c(1e-2, 1e10), ylim = c(0, 1),
  main = sprintf("Comparing across rho values for whole model", am0),
  xlab = "PfEIR [annual log10]", ylab = "PfPR",
  log = "x", type = "l"
)
amchoices <- seq(0, .6, 0.1)
for (am_idx in seq_along(amchoices)) {
  am0 <- amchoices[am_idx]
am <- rep(am0, length(pfpr))
vars <- pixel_two(pfpr, am, k_is_one(params), strategies)
lines(
  vars$aeir, pfpr,
  col = amcol[am_idx]
)
}
legend(
  "bottomright", legend = as.character(amchoices), title = "rho",
  col = amcol[1:length(amchoices)], lty = 1, lwd = 2, cex = 1)
```
```{r variable_by_variable, fig.height = 10, fig.width = 20}
cnt <- 200
pfpr <- 1:cnt/(cnt + 1)
run_one <- function(am) pixel_two(pfpr, rep(am, length(pfpr)), params, strategies)
var_names <- names(run_one(0.1))

flip <- TRUE
par(mfrow = c(2,4))
am_choices <- rev(seq(0, 0.6, 0.1))
vbv_col <- rev(viridis::plasma(length(am_choices), alpha = 1, begin = 0, end = 1))
for (var_name in var_names) {
  for (am_idx in seq_along(am_choices)) {
    am0 <- am_choices[am_idx]
    res <- run_one(am0)
    vary <- res[[var_name]]
    if (flip) {
      y <- pfpr
      x <- vary
      logv <- "x"
      xlab <- var_name
      ylab <- "PfPR"
    } else {
      x <- pfpr
      y <- vary
      logv <- "y"
      xlab <- "PfPR"
      ylab <- var_name
    }
    if (am_idx == 1) {
      plot(
        x, y,
        log = logv, xlab = xlab,
        ylab = ylab, col = vbv_col[am_idx], type = "l")
    } else {
      lines(x, y, type = "l", col = vbv_col[am_idx])
    }
  }
  legend("topleft", legend = sprintf("AM=%3.2f", am_choices), col = vbv_col, lty = 1, lwd = 2, cex = 1)
}
```
```{r}
alpha <- seq(0.01, 0.99, 0.01)
h <- -log(1 - alpha)
plot(alpha, h)
```


Let's try a range of PfPR for one AM.
```{r plot_pfpr_for_an_am, fig.height = 20, fig.width = 10}
cnt <- 200

par(mfrow = c(3,1))
for (am0 in c(0.0, 0.1, 0.5)) {
  pfpr <- 1:cnt/(cnt + 1)
  am <- rep(am0, length(pfpr))
  res <- pixel_two(pfpr, am, params, strategies)
  name <- "alpha"
  plot(
    pfpr, res[[name]],
    xlim = c(0, 1), ylim = c(1e-3, 1e3), log = "y", xlab = "PfPR",
    main = sprintf("AM=%3.2f", am0), ylab = "", col = mcol[name], type = "l")
  not_alpha <- names(res)[!names(res) %in% name]
  for (name in not_alpha) {
    lines(pfpr, res[[name]], type = "l", main = name, ylab = "", col = mcol[name])
  }
  legend("topleft", legend = var_names, col = var_colors, lty = 1, lwd = 2, cex = 1)
}
```
## Testing

```{r test_ar_to_pr_interpolation}
library(testthat)
test_that("rho faster matches", {
  # Using different bounds means we can check that x and y aren't switched.
  rho_grid <- pracma::linspace(-1, 1, 11)
  pr_grid <- pracma::linspace(0, 1, 20)
  testf <- function(x, y) { sin(x) + 2 * cos(y) }
  rho_in <- rep(rho_grid, length(pr_grid))
  pr_in <- rep(pr_grid, each = length(rho_grid))
  zi <- testf(rho_in, pr_in)
  trialf <- ar_of_pr_rho(data.frame(list(rho = rho_in, PR = pr_in, AR = zi)))
  rhot <- c(-0.5, 0.9, -0.1)
  prt <- c(0.9, 0.8, 0.1)
  zt <- trialf(rhot, prt)
  expect_equal(length(zt), length(rhot))
  zpred <- testf(rhot, prt)
  expect_lt(max(abs(zt - zpred)), 0.01)
})
test_that("pr faster matches", {
  # The loop says that as grid gets finer answer gets closer.
  max_miss <- 0.01
  for (i in 0:3) {
    rho_grid <- pracma::linspace(-1, 1, 11 * 2^i)
    pr_grid <- pracma::linspace(0, 1, 20 * 2^i)
    testf <- function(x, y) { sin(x) + 2 * cos(y) }
    pr_in <- rep(pr_grid, length(rho_grid))
    rho_in <- rep(rho_grid, each = length(pr_grid))
    zi <- testf(rho_in, pr_in)
    trialf <- ar_of_pr_rho(data.frame(list(rho = rho_in, PR = pr_in, AR = zi)))
    rhot <- c(-0.5, 0.9, -0.1)
    prt <- c(0.9, 0.8, 0.1)
    zt <- trialf(rhot, prt)
    expect_equal(length(zt), length(rhot))
    zpred <- testf(rhot, prt)
    this_miss <- max(abs(zt - zpred))
    # Ask that convergence be better than linear.
    expect_lt(this_miss, max_miss / 2)
    max_miss <- this_miss
    flog.debug(this_miss)
  }
})
```

